Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-01 manuscript.tex
Adding text to results section

$D$ controls both the accuracy of the integration and the computation time.

The value chosen for $D$ determines how many divisions are made.

@@

To our knowledge,
there has been no further investigation
into the relationship between
values of the distance-size ratio and the computation error.

It is also not clear whether
the same value of $D$ yields compatible error levels
for the gravitational attraction
and the gradient tensor components.

We must determine the relationship between the distance-size ratio $D$ and
the computation error.

We need a reference against which to compare the computed tesseroid fields.

The spherical shell is a convenient reference model.

The spherical shell has a analytical solutions for the gravitational potential,
attraction, and gradient tensor along the polar axis.

\citep{Grombein2013} provides the equations for
the gravitational potential, attraction, and gravity gradient components
of a homogeneous spherical shell.

We used a spherical shell with a thickness of 1 km.

The density of the shell is $2670\ kg.m^{-3}$.

The bottom of the shell is at height 0 km above the reference sphere.

The top of the shell is at 1 km height.

We can use the spherical shell values to calculate the error of the tesseroid
computations for varying values of $D$.

We discretized the spherical shell into tesseroids
with dimensions of $1^\circ \times 1^\circ \times 1\ km$.

We calculate the effect of a tesseroid model on a regular grid.

>>>>

$D$ indirectly controls both the accuracy of the integration
and the computation time.

The specific value chosen for $D$ determines how many divisions will be made
(Figure~\ref{fig:division}).

@@

In this section, we investigate
the relationship between
values of the distance-size ratio
and the computation error.

We perform the error analysis for the gravitational potential,
acceleration, and gradient tensor components
to evaluate if the same value of $D$ yields compatible error levels
for different fields.

We establish a homogeneous spherical shell as a reference against which to
compare the computed tesseroid fields.

The shell has analytical solutions for the gravitational potential,
attraction, and gradient tensor along the polar axis
\citep{Grombein2013}.

We used a spherical shell with a thickness of 1 km,
density of $2670\ kg.m^{-3}$,
bottom at height 0 km above the reference sphere,
and top at 1 km height.

We discretized the spherical shell along the horizontal dimensions into
a regular mesh of tesseroids.

Figure~\ref{fig:glqerrorsample} shows that the largest errors are concentrated
on top of the tesseroid.

If we calculate the tesseroid fields at a single point, that point might not
coincide with the point of largest error.

Performing the error analysis on calculations at a single point will not be
representative of the true error.

Fortunately, the symmetry of the shell allows us to consider the computation point at any
geographic coordinate.

We calculate the effect of the tesseroid model of the spherical shell
on a regular grid.

The effect of the shell will be same along the entire grid.

We perform the analysis on the largest error.
